acquisition of TEs

### 2021-05-17 Analyze_TEs.Rmd
fixed simulation2 figure

## Observed data: Testing Simulation 2
```{r}
plot_stacked_byV <- keepers_ws_TE %>%
  select(baby_id, age_months_percentile, balance_vocab, word_vocab, number_of_te, Dom_unique_words, NonDom_unique_words) %>%
  # Subset developmental level (i.e., Average_90percentile) by 3 levels 
  mutate(V_subset = case_when(age_months_percentile <= 22 ~ "18-22 months (V = 244.9 - 451.9)",
                              age_months_percentile > 22 & age_months_percentile <= 27 ~ "23-27 months (V = 491.8 - 604.1)",
                              TRUE ~ "28-33 months (V = 620.4 - 638.9)")) %>%
  mutate(BalSubset = case_when(balance_vocab >= 0.36 ~ "Most Balanced",
                               balance_vocab <= 0.20 ~ "Least Balanced",
                               TRUE ~ "Medium Balanced")) %>%
  mutate(BalSubset = fct_rev(BalSubset)) %>%
 # mutate(BalSubset = factor(BalSubset, levels=c("Most Balanced", "Medium Balanced", "Least Balanced"))) %>%
  arrange(desc(number_of_te)) %>%
  mutate(TE = number_of_te) %>%
  pivot_longer(-c(baby_id, age_months_percentile, balance_vocab, V_subset, BalSubset, word_vocab, TE), 
               names_to = "Type", values_to = "NumberOfWords") %>%
  mutate(Type = factor(Type, levels=c("NonDom_unique_words", "Dom_unique_words", "number_of_te"))) %>%
  mutate(Type = recode(Type, 
                       NonDom_unique_words = "Initial non-dominant word (NI)", 
                       Dom_unique_words = "Initial dominant word (DI)", 
                       number_of_te = "Translation equivalent (TE)")) %>%
  group_by(age_months_percentile, BalSubset, Type) %>%
  summarise(n_words = mean(NumberOfWords)) %>%
  ggplot(aes(x = BalSubset, y = n_words, fill = Type)) +
  geom_bar(position="stack", stat="identity") +
#  facet_grid(. ~ age_months_percentile) +
  facet_wrap(. ~ age_months_percentile, ncol = 4) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) + 
  scale_x_discrete(labels = function(BalSubset) str_wrap(BalSubset, width = 10)) + 
  ylim(0, 600) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0) , 
        legend.position = "bottom",
        plot.title = element_text(face = 'bold', size = 18, hjust = 0, vjust = 2),
        plot.title.position = "plot",
        text = element_text(size=14),
        panel.spacing.x = unit(2, "lines")) + 
  labs(x = "\nBalance (B)", 
       y = "Number of concepts (C)",
       title = "Panel B: Observed data")

>>>>

## Observed data: Testing Simulation 2
```{r}
plot_stacked_byV <- keepers_ws_TE %>%
  select(baby_id, age_months_percentile, balance_vocab, word_vocab, number_of_te, Dom_unique_words, NonDom_unique_words) %>%
  # Subset developmental level (i.e., Average_90percentile) by 3 levels 
  mutate(V_subset = case_when(age_months_percentile <= 22 ~ "18-22 months (V = 244.9 - 451.9)",
                              age_months_percentile > 22 & age_months_percentile <= 27 ~ "23-27 months (V = 491.8 - 604.1)",
                              TRUE ~ "28-33 months (V = 620.4 - 638.9)")) %>%
  mutate(BalSubset = case_when(balance_vocab >= 0.36 ~ "Most Balanced",
                               balance_vocab <= 0.20 ~ "Least Balanced",
                               TRUE ~ "Medium Balanced")) %>%
  mutate(BalSubset = fct_rev(BalSubset)) %>%
  arrange(desc(number_of_te)) %>%
  mutate(TE = number_of_te) %>%
  pivot_longer(-c(baby_id, age_months_percentile, balance_vocab, V_subset, BalSubset, word_vocab, TE), 
               names_to = "Type", values_to = "NumberOfWords") %>%
  mutate(Type = factor(Type, levels=c("NonDom_unique_words", "Dom_unique_words", "number_of_te"))) %>%
  mutate(Type = recode(Type, 
                       NonDom_unique_words = "Initial non-dominant word (NI)", 
                       Dom_unique_words = "Initial dominant word (DI)", 
                       number_of_te = "Translation equivalent (TE)")) %>%
  group_by(V_subset, BalSubset, Type) %>%
  summarise(n_words = mean(NumberOfWords)) %>%
  ggplot(aes(x = BalSubset, y = n_words, fill = Type)) +
  geom_bar(position="stack", stat="identity") +
  facet_grid(. ~ V_subset) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) + 
  scale_x_discrete(labels = function(BalSubset) str_wrap(BalSubset, width = 10)) + 
  ylim(0, 600) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0) , 
        legend.position = "bottom",
        plot.title = element_text(face = 'bold', size = 18, hjust = 0, vjust = 2),
        plot.title.position = "plot",
        text = element_text(size=14),
        panel.spacing.x = unit(2, "lines")) + 
  labs(x = "\nBalance (B)", 
       y = "Number of concepts (C)",
       title = "Panel B: Observed data")
